\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-23 forwards-and-backwards.tex
done with pass through definitions

Now, let $\beta(x, \eta) = \meanq + 2 \Sigma \grad \log r(x, \eta)$,
and associate with each label an independent $d$-dimensional Brownian motion $W_a$,
and let $\covq = K K^T$.
Then, we can summarize the results above by saying that
in the infinite density limit,
the spatial locations and level of each line of descent $a$
behave for $\tau_a \le t < \sigma_a$ as
\begin{equation*}
\begin{split}
X_a(t)
    &=
    X_a(\tau_a)
    +
    + \int_{\tau_a}^{t}
    \bigg(
        \beta(x, \eta(s)) ds
        +
        K dW_a(s)
    \bigg)
    ds .
\end{split}
\begin{split}
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \delta \gamma(X_a(s),\eta(s))
        r(x,\eta(s)) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
            + F(X_a(s), \eta(s))
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{split}
\end{equation*}
\comment{TODO: add description of Poisson random measure of birth times/levels as below.}

>>>>

\comment{The following could be a Proposition?}

Now, let $\beta(x, \eta) = \meanq + 2 \Sigma \grad \log r(x, \eta)$,
and associate with each label an independent $d$-dimensional Brownian motion $W_a$,
and let $\covq = K K^T$.
Then, we can summarize the results above by saying that
in the infinite density limit,
the spatial locations and level of each line of descent $a$
behave for $\tau_a \le t < \sigma_a$ as
\begin{align*}
X_a(t)
    &=
    X_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \beta(x, \eta(s)) ds
        +
        K dW_a(s)
    \bigg)
    ds  \\
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \delta \gamma(X_a(s),\eta(s))
        r(x,\eta(s)) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
            + F(X_a(s), \eta(s))
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{align*}
To complete the description,
for each label $a \in \labelspace$ let $R_a$ denote an independent Poisson process on $[0, \infty)^2$
with Lebesgue mean measure,
and as before order the points of each in some way.
If the population state at time 0 is $\eta(0)$,
then let $(x_i, u_i)$ be the points of a Poisson process
with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta(0)$ and Lebesgue measure.
\comment{Here I've switched $t$ to be the absolute birth time
rather than relative to the birth time of the parent; I think it's clearer?
It, should be made to agree with the previous section.}
For each point begin a line of descent
with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
Each point in the $R_a$ denotes a potential birth time for $a$:
if the $j^\text{th}$ point in $R_a$ is $(t, v)$,
$\tau_a \ge t$, and and $U_a(t) < \infty$,
then a new line of descent with label $aj$ is produced,
with birth time $\tau_{aj} = t$, location $X_{aj}(t) = X_a(t)$, and level
$$
    U_{aj}(t) = U_a(t)
    + \frac{v}{ 2 \delta \gamma(X_a(t), \eta(t)) r(X_a(t), \eta(t)) } .
$$
\comment{Perhaps the conclusion of the Propostion would be something like:}
We can now express our population processes in the limit using these levels:
\begin{align*}
    \eta_t = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{X_a(t)}
    \qquad \text{and} \qquad
    \lp = \sum_{a : \tau_a > t \;\&\; U_a(t) < \lambda} \delta_{(X_a(t), U_a(t))} .
\end{align*}
